% MIT License
% 
% sec2/section2.tex
% 
% Copyright (c) 2020 冬ノ夜空
% 

\documentclass[10pt,a4j,openany,dvipdfmx]{jsarticle}
\usepackage{docmute} %for "input" command
\input{preamble}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%section%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fundamental Knowledge} % (fold)
\label{sec:fundamental_knowledge}

%@ Image and Container =========================================%
\subsection{Image and Container} % (fold)
\label{sub:image_and_container}

\subsubsection{Dokerfile} % (fold)
\label{ssub:dokerfile}


\begin{tcolorbox}[
title=Dockerfile, fonttitle=\bfseries]
Dockerfileとは、Docker imageのソースコード(設計図)である。
\end{tcolorbox}


% subsubsection dokerfile (end)
\subsubsection{Docker Image} % (fold)
\label{ssub:docker_image}


\begin{tcolorbox}[
title=Docker Image, fonttitle=\bfseries]
Docker imageは基本的にread only。Dockerfileから作成され、幾らかのimage layerから成る。
後述のContainerの核となる部分。
\end{tcolorbox}


% subsubsection docker_image (end)
\subsubsection{Container} % (fold)
\label{ssub:container}


\begin{tcolorbox}[
title=Container, fonttitle=\bfseries]
Containerとは、Docker imageをベースに、(Docker imageの上に) 色々なソフト(database等々)を乗せた、カスタムされた環境のこと。
Docker Engine($\approx$ docker daemon)上で稼働する、packagingされた環境。
\end{tcolorbox}

\begin{skybox}{Docker imageとContainer}
Docker imageは、immutableなContainerのベースイメージ。
Containerは、Docker imageの上に色々なソフト(database等々)を乗せた、カスタムされた環境。
\end{skybox}

\begin{tcolorbox}[
title=docker daemon(dockerd), fonttitle=\bfseries]
dockerd is the persistent process that manages containers. 
\tcblower
dockerd: \url{https://docs.docker.com/engine/reference/commandline/dockerd/}
\end{tcolorbox}

{\Large $\dagger$ Daemon socket}\\
The Docker daemon can listen for Docker Engine API requests via three different types of Socket: unix, tcp, and fd.\\

By default, a unix domain socket (or IPC socket) is created at /var/run/docker.sock,
 requiring either root permission, or docker group membership.\\

If you need to access the Docker daemon remotely, you need to enable the tcp Socket.\\

% subsubsection container (end)


% subsection image_and_container (end)
%@ Image and Container =========================================%


% section fundamental_knowledge (end)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%section%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}


